Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization

### 2019-05-14 presentation/MLPaper.tex
added MLPaper for submission

 \hline
 \multicolumn{1}{|c|}{N-gram} &
 \multicolumn{1}{|c|}{sparsity} &
 \multicolumn{1}{|c|}{smooth$=0.0$} &
 \multicolumn{1}{|c|}{$\alpha=0.002$} &
 \multicolumn{1}{|c|}{$\alpha=1.000$} \\
 \hline
 60& 0.001979 & 0.647 & 0.463 & 0.256\\
 50& 0.002018 & 0.619 & 0.565 & 0.342\\
 30& 0.002038 & 0.724 & 0.620 & 0.460\\
 25& 0.002063 & 0.720 & 0.664 & 0.490\\
 20& 0.002067 & 0.725 & 0.678 & 0.520\\
 12& 0.002069 & 0.682 & 0.743 & 0.656\\
 \hline
\end{tabular}
\end{center}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../output/analysis/unstacked-nb-ll.JPG}
  \caption{F1 performance of LL and NB - Unstacked Model}
\end{figure}

@@

@@

Overall our research found that Logistic Lasso with $\alpha = 0.002$ produced the most stable results for predicting FOMC rate decisions from FOMC statements, minutes, and Board of Governors speeches.

>>>>

 \hline
 \multicolumn{1}{|c|}{N-gram} &
 \multicolumn{1}{|c|}{sparsity} &
 \multicolumn{1}{|c|}{smooth$=0.0$} &
 \multicolumn{1}{|c|}{$\alpha=0.002$} &
 \multicolumn{1}{|c|}{$\alpha=1.000$} \\
 \hline
 60& 0.001979 & 0.647 & 0.463 & 0.256\\
 50& 0.002018 & 0.619 & 0.565 & 0.342\\
 30& 0.002038 & 0.724 & 0.620 & 0.460\\
 25& 0.002063 & 0.720 & 0.664 & 0.490\\
 20& 0.002067 & 0.725 & 0.678 & 0.520\\
 12& 0.002069 & 0.682 & 0.743 & 0.656\\
 \hline
\end{tabular}
\end{center}
\vertSpace
\noindent Below is a plot showing Naive Bayes giving consistent results relative
to Logistic Lasso .

\begin{figure}[h!]
  \centering
  \includegraphics[width=100mm]{./ngramlen_nb_ll.pdf}
  \caption{F1 performance of LL and NB - Unstacked Model}
\end{figure}

\subsubsection{Impact of N-gram sequences on results}
We varied the N-gram sequences to observe its impact on out of sample prediction.  There is a definite range of N-gram sequences where all of the models greatly improved. 
All of the models showed great improvement when the n-gram sequences ranged between 4:6 and 10:15.  As the sequences started getting larger than 20 words, the results
started to fall off as Feature matricies became more sparse.  Below is a graph of various both Logistic Lasso and Naive Bayes plotted for
different regularizaion coefficients while varying the N-gram sequence.  The interesting part about this is Federal Reserve commentary tends to have sequences
of hawkish or dovish sentiment which can't be expressed in a few words which might be the reason why smaller n-gram sequences did not perform as well.
\begin{figure}[h!]
  \centering
  \includegraphics[width=100mm]{./ngram_seq.pdf}
  \caption{N-gram sequence LL and NB - Stacked Model}
\end{figure}
\vfill

@@

We found that n-gram sequences of varying between 4:7 to 10:15 provided the best results. Smaller n-gram sequences ($< 4$ words) and larger sequences ($>20$ do to extreme sparsity) did not generate good results.

@@

Overall our research found that Logistic Lasso with smaller penalty $\alpha < 0.02$ produced the most stable results for predicting FOMC rate decisions from FOMC statements, minutes, and Board of Governors speeches.

The limitation in this study is the size of the data sets. While we were able to identify charactersistics that would help predictive power the strength of the conclusions are tempered by the amount of data on hand.
